### 2025-09-18 correlation.qmd
20250903 - fix computational challenges
20250918 - edit

- there is low variability in one or both variables (i.e., [restricted range](#sec-correlationRestrictedRange))
- the two distributions show dissimilar shapes (in terms of [skewness and kurtosis](#sec-descriptiveStatisticsShape))
- the underlying association is nonlinear, such that [Pearson](#sec-correlationExamplesPearson) correlation does not capture the association
- [outliers](#sec-correlationOutliers) weaken the apparent linear trend
- the association differs across subgroups of the sample
- the data contain random measurement error

@@

correlation::correlation(
  data = player_stats_seasonal %>% select(draft_round, fantasyPoints),
  method = "distance"
)
```

>>>>

- there is low variability in one or both variables (i.e., [restricted range](#sec-correlationRestrictedRange))
- the two distributions show dissimilar shapes (in terms of [skewness and kurtosis](#sec-descriptiveStatisticsShape))
- the underlying association is nonlinear, such that [Pearson](#sec-correlationExamplesPearson) correlation does not capture the association
- [outliers](#sec-correlationOutliers) weaken the apparent linear trend
- the association differs across subgroups of the sample (i.e., [moderation](#sec-moderation))
- the data contain random measurement error

@@

correlation::correlation(
  data = player_stats_seasonal %>% 
    filter(season == max(season, na.rm = TRUE)) %>% 
    select(draft_round, fantasyPoints),
  method = "distance"
)
```
